Self Regulation Ontology Retest Analyses

### 2018-06-07 code/SRO_Retest_Analyses.Rmd
working on explaining the noise ceiling results with loocv results

### Direct relation to our results

@@

Are the differences in the distributions significant?
The literature does a better job in predicting itself for tasks compared to surveys. s

@@

Our data is better in predicting the literature estimates for the surveys that it is in predicting tasks.

@@

>>>>

### Correlation with our results

@@

Are the differences in the distributions significant?
There is a significant interaction, such that...

```{r}
tmp = comp_lit_pred_out_both %>%
  select(-.n, -m_lit, -m_boot) %>%
  gather(key, value, -task)

summary(lm(value ~ key*task, tmp))
```

The literature does a better job in predicting itself for tasks compared to surveys (comparing the two orange distributions).

@@

Our data is better in predicting the literature estimates for the surveys that it is in predicting tasks (comparing the difference between orange and purple for red and blue outlines).

@@

Why are the reliability estimates from surveys worse compared to tasks in predicting the literature?

Rank by variance: empirical estimates for surveys < literature estimates for surveys < empirical estimates for tasks < literature estimates for tasks

In this procedure having high variance is better. When predicting the literature using an empirical estimate for a survey measure

```{r}
rel_comp %>%
  select(task, retest_reliability, mean_pearson) %>%
  gather(key, value, -task) %>%
  group_by(key, task) %>%
  summarise(variance = var(value)) %>%
  ungroup()%>%
  mutate(key = ifelse(key == "mean_pearson", "emp", "lit")) %>%
  arrange(variance)
```
